%% Bade_Naveen_Kumar_WiproCOE_Resume.tex
%% ATS-Compliant One-Page Resume — Wipro COE ELITE | 2026 | FY'27 (Project Engineer)
%% Compile with: pdflatex Bade_Naveen_Kumar_WiproCOE_Resume.tex

\documentclass[10pt,a4paper]{article}

%% ---------- packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.55in, top=0.45in, bottom=0.45in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{array}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{parskip}

%% ---------- colours ----------
\definecolor{accent}{HTML}{1A237E}   % dark indigo — ATS safe (printed as black)

%% ---------- hyperref ----------
\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent,
  pdfauthor={Bade Naveen Kumar},
  pdftitle={Bade Naveen Kumar — Wipro COE ELITE Resume}
}

%% ---------- section formatting ----------
\titleformat{\section}
  {\bfseries\large\color{accent}}
  {}{0em}{}
  [\color{accent}\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

%% ---------- helpers ----------
\newcommand{\entry}[4]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} — \textit{#2} & \textbf{#3}
  \end{tabularx}
  \vspace{1pt}#4\vspace{4pt}
}

\newcommand{\projentry}[3]{%
  \noindent\textbf{#1} \hfill \textit{#2}
  \vspace{1pt}#3\vspace{4pt}
}

\setlist[itemize]{leftmargin=1.2em, topsep=2pt, itemsep=0pt, parsep=0pt}

\pagestyle{empty}

%% ==========================================================================
\begin{document}

%% ===== HEADER ===============================================================
\begin{center}
  {\LARGE\bfseries BADE NAVEEN KUMAR}\\[3pt]
  Bhubaneswar, Odisha, India\ \ $\vert$\ \
  \href{mailto:badenaveenkumar@gmail.com}{badenaveenkumar@gmail.com}\ \ $\vert$\ \
  +91-XXXXXXXXXX\\[2pt]   %% TODO: replace with actual mobile number
  \href{https://linkedin.com/in/bade-naveen-kumar}{linkedin.com/in/bade-naveen-kumar}\ \ $\vert$\ \
  \href{https://github.com/BadeNaveenKumar}{github.com/BadeNaveenKumar}
\end{center}

\vspace{2pt}

%% ===== PROFILE SUMMARY ======================================================
\section{Profile Summary}
Motivated Computer Science \& Engineering (IoT) final-year student with hands-on experience building
end-to-end data pipelines, interactive dashboards, and Python automation tools.
Adept at translating raw datasets into actionable business intelligence using SQL, Power~BI, and Python.
Supplementary skills in embedded/IoT systems and a disciplined background as an NNC~Cadet make me a
well-rounded candidate for Wipro's Project~Engineer (COE~ELITE) role, where I am eager to contribute
to impactful engineering and analytics projects from day one.

%% ===== EDUCATION ============================================================
\section{Education}
\entry{Siksha `O' Anusandhan University}{B.Tech — CSE (IoT) \quad CGPA: 7.2/10}{2022 -- 2026}{}

\vspace{-2pt}
\noindent
\begin{tabularx}{\linewidth}{@{}X X@{}}
  \textbf{Class XII (CBSE/State Board)} — Science (PCM) & \textbf{Class X (CBSE/State Board)} \\
  Percentage: \textit{XX\%} \hfill Year: 20XX & Percentage: \textit{XX\%} \hfill Year: 20XX
  %% TODO: replace XX% and 20XX with actual board, percentage and year
\end{tabularx}

%% ===== TECHNICAL SKILLS =====================================================
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textbf{Languages}        & Python, SQL, C/C++, Bash \\
  \textbf{Data \& Analytics}& Pandas, NumPy, Matplotlib, Seaborn, Plotly, Power~BI, Tableau, Excel \\
  \textbf{Databases}        & MySQL, PostgreSQL, SQLite \\
  \textbf{Embedded / IoT}   & Arduino, Raspberry~Pi, Sensor interfacing, MQTT, I2C/SPI protocols \\
  \textbf{Automation \& ETL}& Apache~Airflow (basics), Cron, Pytest, Selenium \\
  \textbf{Tools / Platforms}& Git, GitHub, Jupyter, VS~Code, Linux, MS~Office \\
  \textbf{Concepts}         & Data Pipeline Design, Dashboard Development, MIS Reporting, A/B Testing \\
\end{tabularx}

%% ===== PROJECTS =============================================================
\section{Projects}

\projentry{E-Commerce Retention Analytics Platform}{Python $\cdot$ SQL $\cdot$ Power BI $\cdot$ Pandas}{
\begin{itemize}
  \item Engineered an end-to-end ETL pipeline ingesting 50\,000+ transaction records; reduced data
        preparation time by 40\%.
  \item Built cohort-retention and RFM-segmentation models revealing a 22\% churn rate in the
        90-day window, informing targeted re-engagement campaigns.
  \item Developed an interactive Power~BI dashboard with 8 KPI tiles (revenue, AOV, CLV, churn)
        enabling stakeholders to drill down by segment, region, and time period.
\end{itemize}
}

\projentry{Data Pipeline \& Retail Sales Analytics}{Python $\cdot$ MySQL $\cdot$ Apache Airflow $\cdot$ Matplotlib}{
\begin{itemize}
  \item Designed an automated daily data pipeline that cleansed, validated, and loaded retail sales
        data from CSV/API sources into a relational database with 99\%+ data accuracy.
  \item Generated automated MIS reports (weekly/monthly) covering sales trends, inventory turnover,
        and forecasting, reducing manual reporting effort by $\sim$3 hours/week.
  \item Applied A/B testing on marketing campaigns, identifying a 15\% uplift from personalised
        discount offers using statistical significance tests.
\end{itemize}
}

\projentry{Embedded IoT Sensor Monitor}{C $\cdot$ Python $\cdot$ Raspberry Pi $\cdot$ MQTT}{
\begin{itemize}
  \item Developed a real-time sensor monitoring system (temperature, humidity, gas) using Raspberry~Pi
        and multiple I2C/SPI sensors with MQTT-based data streaming.
  \item Implemented threshold-based alert logic and a lightweight Python dashboard for live telemetry
        visualisation, reducing anomaly detection lag to under 2~seconds.
  \item Documented hardware schematics and firmware, enabling seamless handoff and future
        extensibility.
\end{itemize}
}

%% ===== CERTIFICATIONS =======================================================
\section{Certifications}
\begin{itemize}
  \item \textbf{Python for Data Science} — NPTEL / Coursera \hfill \textit{20XX} %% TODO: add year
  \item \textbf{Data Analytics with Python} — IBM / Cognitive Class \hfill \textit{20XX}
  \item \textbf{SQL for Data Science} — UC Davis / Coursera \hfill \textit{20XX}
  \item \textbf{Power BI Data Analyst Associate} — Microsoft (PL-300 preparation) \hfill \textit{20XX}
  \item \textbf{Introduction to IoT} — Cisco Networking Academy \hfill \textit{20XX}
  \item \textbf{NNC (Naval Cadet Corps) Certificate} — Ministry of Defence, Government of India
        \hfill \textit{20XX}
  %% TODO: fill in actual years above and add any certificates from attached images below
  %% \item \textbf{[Certificate from Image 1]} — [Issuer] \hfill [Year]
\end{itemize}

%% ===== ACHIEVEMENTS ==========================================================
\section{Achievements}
\begin{itemize}
  \item \textbf{NCC / NNC Cadet Recognition} — Awarded for exemplary discipline, leadership, and
        service as a Naval Cadet, demonstrating teamwork and responsibility under structured training.
  \item \textbf{Academic Excellence} — Maintained a consistent CGPA of 7.2/10 while simultaneously
        managing engineering projects and extracurricular commitments.
  \item \textbf{Open-Source Contributor} — Maintained the \textit{Ecommerce-retention-analytics}
        GitHub repository with documented ETL pipelines, dashboards, and A/B testing modules.
  %% TODO: add any awards / hackathon wins from certificate images here, e.g.:
  %% \item \textbf{[Award Name]} — [Event / Organisation] \hfill [Year]
\end{itemize}

%% ===== ADDITIONAL ACTIVITIES ================================================
\section{Additional Activities}
\begin{itemize}
  \item \textbf{NNC (Naval Cadet Corps)} — Active cadet; participated in national camps,
        discipline drills, and community service drives, building strong leadership and
        team-management skills.
  \item \textbf{Technical Volunteer} — Assisted in organising department-level data-science
        workshops and hackathons at Siksha `O' Anusandhan University.
\end{itemize}

\end{document}
